\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
\raggedright


\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% BEGIN RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-20pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        \vspace*{5pt}
        #2 \\ #3
    \end{center}
    \vspace*{-10pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

    \vspace*{-40pt}

    \contact{Full Name}
    {Some City, ST, 05550 $\cdot$ (505)~555~5050 \\
    first@firstlast.com $\cdot$ github.com/firstlast}

    %%%%%%%%%%%%%%%
    %% Education %%
    %%%%%%%%%%%%%%%

    \header{Education}
        \vspace{1mm}
        \textbf{Some University} \hfill \textit{BS Computer Science} \hfill Some City, ST \hfill Expected: May 2017\\

    \vspace{3mm}

    %%%%%%%%%%%%%%%%%%%%%
    %% Work Experience %%
    %%%%%%%%%%%%%%%%%%%%%

    \header{Work Experience}
        \vspace{1mm}

        \textbf{Some Company} \hfill \textit{Software Engineer Intern} \hfill Some City, ST \hfill Jun 2016 | Aug 2016 \\
        \begin{itemize} \itemsep 3pt
            \item Improved search and autofill components to include subdomains.
            \item Refactored and simplified APIs to use existing components and minimize code duplication.
            \item Fixed regressions and improved testing to prevent them in the future.
        \end{itemize}

        \vspace{1mm}

        \textbf{Some Company} \hfill \textit{Coding Advisor} \hfill Some City, ST \hfill Dec 2015 | May 2016 \\
        \begin{itemize} \itemsep 3pt
            \item Created a JavaScript project in the new JS course for premium members.
            \item Taught new coders how to avoid bugs and how to go through the process of fixing existing ones.
            \item Reviewed general programming topics with students and provided assistance for lessons in Java, HTML, CSS, JavaScript, and Ruby.
        \end{itemize}

        \vspace{1mm}

        \textbf{Some Company} \hfill \textit{Software Developer Intern} \hfill Some City, ST \hfill Jun 2015 | Nov 2015 \\
        \begin{itemize} \itemsep 3pt
            \item Wrote an API that allowed CRUD operations to be used for accessing and manipulating data involving current departments/groups/teams at company.
            \item Created a UI for admins that used the aforementioned API to automate the process of syncing departments/groups/teams on the site to relevant databases.
            \item Improved the company site by using cookies to display tailored web-content.
        \end{itemize}

        \vspace{1mm}

        \textbf{Some Company} \hfill \textit{Web Developer Intern} \hfill Some City, ST \hfill Jan 2015 | Jun 2015 \\
        \begin{itemize} \itemsep 3pt
            \item Improved existing web pages by migrating inline-styling to external CSS files, and adding cross-browser compatibility.
            \item Created front-ends with HTML, CSS, and JavaScript and utilized the jQuery UI library to create responsive widgets.
            \item Debugged original code base as the sole developer on the team and created a standard for web part development for future employees.
        \end{itemize}

        \vspace{1mm}


    %%%%%%%%%%%%
    %% Skills %%
    %%%%%%%%%%%%

    \header{Skills}

    {Programming Languages:} $\:$ JavaScript, Java, Ruby, HTML, XML, CSS, Sass \vspace{1mm}
    {\\Frameworks/Libraries:} $\:$ $\:$ $\:$ $\:$Node.js, Koa, Express, Sinatra, React, Redux, jQuery, lodash

    \vspace{4mm}

    %%%%%%%%%%%%%%
    %% Projects %%
    %%%%%%%%%%%%%%

    \header{Projects}
    Source code and other projects available at \textit{github.com/firstlast} \\

    \vspace{2mm}

    \textbf{Resume Generator} \textit{Node.js, Koa, React, Redux} \\
    A webapp for generating LaTeX resumes from form data (including this one). \\

    \vspace{2mm}

    \textbf{Cube Timer} \textit{Node.js, Koa, React, Redux, PostgreSQL}  \hfill \\
    A modern speedcubing app with a scrambler, timer, and analyzer for cubing statistics. \\

    \vspace{2mm}

    \textbf{Reddit Scraper} \textit{Ruby, Sinatra} \hfill \\
    A web app that lets you view a collage of images/videos from a subreddit

    \vspace{2mm}

    \textbf{Invoice Generator} \textit{JavaScript, Chrome APIs}  \hfill \\
    A chrome extension used to automate the process of generating an invoice at X company. \    \

    \vspace{2mm}

    {\textbf{Themes} \textit{XML, JSON} \hfill \\
    A collection of custom themes for Sublime Text with 30k+ installations.

\end{document}
